Author Guidelines for DAGM-OAGM Submission

### 2013-08-16 itm/paper.tex
make tables more consistent
making figures larger
Add inferred dimensions to the itm paper...

\begin{algorithm}[t]
\caption{Information Theoretic MST-based Clustering}

\begin{algorithmic}\label{overall}
    \Require Points $\mathbf{x}$, desired number of clusters $k$.
    \Ensure Clustering $\mathbf{y}$ of $\mathbf{x}$
    \State $G \leftarrow T(\mathbf{x})$
    \For{$i=0,\dotsc,k-1$}
        \For{$G_j, j=0,\dotsc, i$ connected components of $G$}
            \State $e_j \leftarrow \text{SplitCluster}(G_j)$
        \EndFor
        \State $l \leftarrow \displaystyle \argmax_j\  \hat{I}(G_j \setminus e_j)$
        \State $G \leftarrow G \setminus e_l$
    \EndFor
    \Statex
    \Function{SplitCluster}{$G$}
        %\Require Euclidean minimum spanning tree $T$, dimension $d$
        %\Ensure $e^* = \displaystyle \argmax_{e\in E(T)} \ \hat{I}(G \setminus e )$
        \State Pick arbitrary root $x_0$ of $G$.
        \For{node $x$ starting from leaves}
            \State $w_x \leftarrow \displaystyle \sum_{c \in \text{children}(x)} w_c + d(x, c)$
            \State $n_x \leftarrow \displaystyle 1 + \sum_{c \in \text{children}(x)} n_c$
        \EndFor
        \For{node $x$ starting from root}
        \State $w'_x \leftarrow w'_{\text{par}(x)} + w_{\text{par}(x)} - w_x + d(x, \text{par}(x))$
        \EndFor
        \For{$e \in E(G), e=(c, p)$, $p$ parent of $c$}
            \State $v_c \leftarrow w'_p + w_p - w_c - d(p,c)$
            \State $m_c \leftarrow n - n_c$
            \State objective$(e) \leftarrow d m_c \ln(m_c) - (d-1) m_c \ln(v_c) + d n_c \ln(n_c) - (d-1) n_c \ln (w_c)$
        \EndFor
        \State $e^* \leftarrow \displaystyle \argmax_{e \in E(G)} \ \text{objective}(e)$

    \EndFunction
\end{algorithmic}
\end{algorithm}

@@

\begin{figure}
\centering
\includegraphics[width=.3\textwidth]{illustration_left}
\includegraphics[width=.3\textwidth]{illustration_center}
\includegraphics[width=.3\textwidth]{illustration_right}
\caption{Illustration of the optimization algorithm for $k=3$ on synthetic
dataset. \emph{Left}: Euclidean minimum spanning tree of the data.
\emph{Center}: The edge that yields the best two-cluster partition in terms of
\eqref{objective} was removed, yielding two connected components. \emph{Right}:
Another edge from the forest was removed, resulting in the desired number of
three components. Note that the edge that are removed are not the longest edges
but form a trade-off between edge length and cluster size.}
\label{fig:illustration}
\end{figure}

@@

We use the dual-tree Boruvka algorithm~\citep{dtb2010} to compute the minimum
spanning tree, which has runtime close to $O(n \log(n) \alpha(n))$. Here
$\alpha$ is the inverse of the Ackerman function, which grows so slowly as to
be considered constant in practice. The dynamic programming solution of
Algorithm~1 has a run time of $O(n)$ per removed edge, leading to an overall
run time of $O(n \log(n) \alpha(n)+ nk)$. The $O(nk)$ comes from a worst case
scenario, in which each step in the hierarchical clustering procedure only
splits off a constant number of points. In a more realistic setting, we expect
that the individual clusters are much smaller than the original dataset. In
this case, the $O(nk)$ factor would improve to $O(n\log(k))$.

\begin{figure}[t]
\centering
\includegraphics[width=.2\textwidth]{qualitative_blobs_km}
\includegraphics[width=.2\textwidth]{qualitative_blobs_mean_nn}
\includegraphics[width=.2\textwidth]{qualitative_blobs_aggl}
\includegraphics[width=.2\textwidth]{qualitative_blobs_mst} \\

\includegraphics[width=.2\textwidth]{qualitative_circles_km}
\includegraphics[width=.2\textwidth]{qualitative_circles_mean_nn}
\includegraphics[width=.2\textwidth]{qualitative_circles_aggl}
\includegraphics[width=.2\textwidth]{qualitative_circles_mst} \\

\includegraphics[width=.2\textwidth]{qualitative_circles2_km}
\includegraphics[width=.2\textwidth]{qualitative_circles2_mean_nn}
\includegraphics[width=.2\textwidth]{qualitative_circles2_aggl}
\includegraphics[width=.2\textwidth]{qualitative_circles2_mst} \\

\includegraphics[width=.2\textwidth]{qualitative_twomoons_km}
\includegraphics[width=.2\textwidth]{qualitative_twomoons_mean_nn}
\includegraphics[width=.2\textwidth]{qualitative_twomoons_aggl}
\includegraphics[width=.2\textwidth]{qualitative_twomoons_mst} \\ 
\caption{Comparison of $k$-Means (left), MeanNN (center left), single link
(center right) and ITM (right) on four synthetic datasets.  Without the need to
tune parameters, ITM can adjust to different cluster shapes.  MeanNN is able to
recover non-convex clusters (third row) but often produces similar results to
$k$-Means (second and last row). Single link clustering is very sensitive
to noise, as it does not take cluster size into account.}
\label{fig:qualitative}
\end{figure}

@@

A comparison of ITM, MeanNN and the baseline methods, $k$-Means and 
single link agglomerative clustering, in terms of their objective, 
optimization and complexity can be found in Table~\ref{nowotab}. 
We implemented the ITM clustering procedure as well as MeanNN in Python.  We
used the $k$-Means implementation available in the scikit-learn
library~\citep{pedregosa2011scikit}.  We use the dual tree Boruvka algorithm
implemented in the mlpack machine learning library~\citep{mlpack2011}. The source
code is available online\footnote{\url{https://github.com/amueller/information-theoretic-mst}}.

@@

\begin{table}[t]
\caption{Comparing properties of related algorithms.}\label{nowotab}
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lccc}
\toprule
Algorithm &     Objective &     Deterministic&      Complexity \\
\cmidrule{1-4}
$k$-Means &     $\displaystyle \sum_y \sum_{i, y_i = y} \| x_i - \mu_y \|^2$ & No  & $O(nk)$ per iteration
%\footnote{The worst-time complexity of the Lloyd-Algorithm is exponential~\cite{arthur2006slow}, though online algorithm are observed to converge in linear time~\cite{bottou1995convergence}.}
\\
MeanNN &    $\displaystyle \sum_y \log\left(\frac{1}{|\mathbf{x}_y|}\sum_{i,j, y_i=y_j=y} \| x_i - x_j \|^2 \right)$ & No & $O(n^2)$ per iteration\\
Single Link &   -- &    Yes    &    $O(n\log n)$\\
ITM & $\displaystyle \sum_{y=0}^k d p(y) \log(\bar{L}_y  ) + p(y) \log{p(y)}$ & Yes & $O(\alpha(n) n \log n + nk)$\\
\bottomrule
\end{tabularx}
\end{table}

@@

We evaluated the experiments using the \emph{adjusted Rand index 
(ARI}~\citep{hubert1985comparing} and \emph{normalized mutual
information (NMI)}~\citep{strehl2003cluster}, two popular measures 
of cluster quality~\citep{gomes2010discriminative,kamvar2003spectral}.
The Rand index~\citep{rand1971objective} between two clusterings counts on how
many pairs of points two clusterings agree. The adjusted Rand index contains a
calibration against chance performance.

Table~\ref{results} summarizes the results. The two entropy-based methods 
(MeanNN, ITM) have a clear advantage of the other methods, with ITM finding 
better clusterings than MeanNN in the majority of cases. 
%
The single link agglomerative clustering procedure produces reasonable 
results on datasets with little noise and well-separated clusters, but 
fails otherwise.
%
When inspecting the results, we observed that ITM produced several very small
clusters on the \emph{faces} dataset. Indeed, increasing the minimum cluster 
size to 6 or more improved the results to 0.59/0.84. A possible explanation 
for this is that very small clusters make the entropy estimate less reliable. 
%
The single-link method also benefited from this, improving its results to 
0.42/0.82.
The run time of computing the ITM clustering was dominated by the computation
of the MST of the data. The implementation in mlpack took
60 seconds on a desktop computer for \emph{usps}, the largest dataset in our 
experiments.
%
The other methods had run times in the order of seconds, but given the 
different implementations we used, this should not be interpreted as a 
general statement about the speed of the individual methods.

\begin{table}[t]
\caption{Scores (ARI/NMI) of $k$-Means, MeanNN, single link agglomerative clustering and
ITM on several benchmark datasets (higher is better). The best score for
each dataset is printed in bold.}\label{results}
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lrrrcccc}
\toprule
\multicolumn{4}{c}{Dataset} &\multicolumn{4}{c}{Results}\\
\cmidrule{1-4}
\cmidrule{5-8}
Description &     n &    d &   k &  $k$-Means        & MeanNN                & SL                       &   ITM\\
\cmidrule{1-4}                   \cmidrule{5-5}      \cmidrule{6-6}          \cmidrule{7-7}             \cmidrule{8-8}
digits      &  1797 &   64 &  10 &     0.62\,/\,0.71 &    0.67\,/\,0.76      &0.10\,/\,0.50             &\B{0.85}\,/\,\B{0.89}\\ 
faces       &   400 & 4096 &  40 &     0.41\,/\,0.76 & \B{0.49}\,/\,\B{0.80} &0.08\,/\,0.69             &0.02\,/\,0.49\\ %\footnotemark[4]
iris        &   150 &    4 &   3 &     0.72\,/\,0.76 &    0.75\,/\,0.78      &0.55\,/\,0.72             &\B{0.88}\,/\,\B{0.87}\\
usps        &  9298 &  256 &  10 &     0.52\,/\,0.61 & \B{0.54}\,/\,\B{0.65} &0.00\,/\,0.04             &   0.44\,/\,0.58\\ 
vehicle     &   846 &   18 &   4 &     0.10\,/\,0.15 &    0.09\,/\,0.11      &0.00\,/\,0.04             &\B{0.10}\,/\,\B{0.14}\\
vowel       &   990 &   10 &  11 &     0.17\,/\,0.37 &    0.19\,/\,\B{0.40}  &0.00\,/\,0.16             &\B{0.20}\,/\,0.39\\
waveform    &  5000 &   21 &   2 & \B{0.37}\,/\,0.35 &    0.30\,/\,\B{0.38}  &0.00\,/\,0.00             &    0.23\,/\,0.22\\
\bottomrule
\end{tabularx}
\end{table}

% TODO more experiments: mnist / usps
% TODO intrinsic dimensionality
% todo segmentation unsupervised
% TODO bag of word experiment?

\section{Summary}
In this summary we proposed the use of a minimum spanning tree based,
non-parametric entropy estimator in information theoretic clustering, ITM\@.
Thereby we extended the work of \citet{faivishevsky2010nonparametric} to a more
flexible and efficient entropy estimate.  We proposed an approximate optimization
method by formulating the clustering problem as a search over graphs.
The resulting algorithm is deterministic has sub-quadratic run time.
%
Empirical comparisons showed that the proposed method outperforms standard
algorithms and the non-parametric entropy based clustering of
\citep{faivishevsky2010nonparametric} on multiple benchmark datasets. We
demonstrated that ITM is able to detect non-convex clusters,
even in the presence of noise.
%
In contrast to other algorithms that can handle non-convex clusters, ITM has no
tuning parameters, as the objective presents a natural trade-off between
balancing cluster sizes and enforcing intra-cluster similarity.

%A limitation of the proposed algorithm is that it is based on the assumption 
%of an absolute continuous data distribution. This assumption eliminates the 
%possibility of using categorical variables and data that lies on a submanifold 
%of the input space. 
%
%In future work we plan to investigate a way to overcome this limitation, 
%for example by estimating the intrinsic dimensionality of the 
%data~\citep{pettis1979intrinsic}.
%
%We will also investigate optimizations of the objective 
%\eqref{graphobjective} that go beyond the proposed method. 
%Move-making algorithms seem a promising way to refine solutions 
%found by Algorithm~1. Branch and bound techniques could provide 
%an alternative approach.

>>>>

\begin{algorithm}[t]
\begin{algorithmic}\label{overall}
    \Require Points $\mathbf{x}$, desired number of clusters $k$.
    \Ensure Clustering $\mathbf{y}$ of $\mathbf{x}$
    \State $G \leftarrow T(\mathbf{x})$
    \For{$i=0,\dotsc,k-1$}
        \For{$G_j, j=0,\dotsc, i$ connected components of $G$}
            \State $e_j \leftarrow \text{SplitCluster}(G_j)$
        \EndFor
        \State $l \leftarrow \displaystyle \argmax_j\  \hat{I}(G_j \setminus e_j)$
        \State $G \leftarrow G \setminus e_l$
    \EndFor
    \Statex
    \Function{SplitCluster}{$G$}
        %\Require Euclidean minimum spanning tree $T$, dimension $d$
        %\Ensure $e^* = \displaystyle \argmax_{e\in E(T)} \ \hat{I}(G \setminus e )$
        \State Pick arbitrary root $x_0$ of $G$.
        \For{node $x$ starting from leaves}
            \State $w_x \leftarrow \displaystyle \sum_{c \in \text{children}(x)} w_c + d(x, c)$
            \State $n_x \leftarrow \displaystyle 1 + \sum_{c \in \text{children}(x)} n_c$
        \EndFor
        \For{node $x$ starting from root}
        \State $w'_x \leftarrow w'_{\text{par}(x)} + w_{\text{par}(x)} - w_x + d(x, \text{par}(x))$
        \EndFor
        \For{$e \in E(G), e=(c, p)$, $p$ parent of $c$}
            \State $v_c \leftarrow w'_p + w_p - w_c - d(p,c)$
            \State $m_c \leftarrow n - n_c$
            \State objective$(e) \leftarrow d m_c \ln(m_c) - (d-1) m_c \ln(v_c) + d n_c \ln(n_c) - (d-1) n_c \ln (w_c)$
        \EndFor
        \State $e^* \leftarrow \displaystyle \argmax_{e \in E(G)} \ \text{objective}(e)$

    \EndFunction
\end{algorithmic}
\caption{Information Theoretic MST-based Clustering}

\end{algorithm}

@@

\begin{figure}
\centering
\includegraphics[width=.30\textwidth]{illustration_left}
\includegraphics[width=.30\textwidth]{illustration_center}
\includegraphics[width=.30\textwidth]{illustration_right}
\caption{Illustration of the optimization algorithm for $k=3$ on synthetic
dataset. \emph{Left}: Euclidean minimum spanning tree of the data.
\emph{Center}: The edge that yields the best two-cluster partition in terms of
\eqref{objective} was removed, yielding two connected components. \emph{Right}:
Another edge from the forest was removed, resulting in the desired number of
three components. Note that the edge that are removed are not the longest edges
but form a trade-off between edge length and cluster size.}
\label{fig:illustration}
\end{figure}

@@

We use Prim's algorithm combined with a ball tree data structure for distance
queries to compute the minimum spanning tree of the data.
While this procedure has no strong guarantees, we found this faster
in practice than specialized algorithms for euclidean minimum spanning trees, 
which achive a better theoretical runtim of $O(n \log(n) \alpha(n))$~\citep{dtb2010}. Here
$\alpha$ is the inverse of the Ackerman function. The dynamic programming solution of
Algorithm~1 has a run time of $O(n)$ per removed edge, leading to an overall
run time of $O(n \log(n) \alpha(n)+ nk)$. The $O(nk)$ comes from a worst case
scenario, in which each step in the hierarchical clustering procedure only
splits off a constant number of points. In a more realistic setting, we expect
that the individual clusters are much smaller than the original dataset. In
this case, the $O(nk)$ factor would improve to $O(n\log(k))$.

\subsection{Estimating Intrinsic Dimensionality}
While assuming totally continuous densities is very natural from a theoretical
point of view, it can be a hindrance in practical applications.  Often, the
data is assumed to lie on a lower-dimensional manifold, embedded in a
higher-dimensional space. In this case, the density is not totally continuous,
and the dimensionality of the data can not be taken as the dimensionality of
the embedding space.

A particularly drastic example is the case of the dataset having less samples
than features. In this case, the data clearly lies even on a linear subspace
of the input space, and the dimensionality of the input space does not
accurately reflect the intrinsic dimensionality of the data.
We use the estimate analyzed in \citet{massoud2007manifold}.
In their method, for each datapoint $x$, a local estimate $\hat{d}(x)$ of the
dimensionality at $x$ is computed as
\begin{equation}
    \hat{d}(x) = \frac{\ln 2}{\ln(r_k(x) / r_{\lfloor k /2 \rfloor}(x)}.
\end{equation}
Here $k$ is a fixed integer and $r_k(x)$ is the distance of $x$ from its $k$th neighbor.
We follow \citet{massoud2007manifold} and set $k =\lceil 2 \ln n\rceil$.
The final estimate $\hat{d}$ is then computed by averaging the estimates over all $x$
\begin{equation}
    \hat{d} = \frac{1}{n}\sum_{x \in X} \min\left(\hat{d}(x),\ d\right).
\end{equation}
We found this estimate to work robustly and give sensible results in all setting.
As we already used a ball-tree data structure to build the minimum spanning trees,
estimating the dimensionality resulted in neglectible computational overhead.

\begin{figure}[t]
\centering
\includegraphics[width=.24\textwidth]{qualitative_blobs_km}
\includegraphics[width=.24\textwidth]{qualitative_blobs_mean_nn}
\includegraphics[width=.24\textwidth]{qualitative_blobs_aggl}
\includegraphics[width=.24\textwidth]{qualitative_blobs_mst} \\

\includegraphics[width=.24\textwidth]{qualitative_circles_km}
\includegraphics[width=.24\textwidth]{qualitative_circles_mean_nn}
\includegraphics[width=.24\textwidth]{qualitative_circles_aggl}
\includegraphics[width=.24\textwidth]{qualitative_circles_mst} \\

\includegraphics[width=.24\textwidth]{qualitative_circles2_km}
\includegraphics[width=.24\textwidth]{qualitative_circles2_mean_nn}
\includegraphics[width=.24\textwidth]{qualitative_circles2_aggl}
\includegraphics[width=.24\textwidth]{qualitative_circles2_mst} \\

\includegraphics[width=.24\textwidth]{qualitative_twomoons_km}
\includegraphics[width=.24\textwidth]{qualitative_twomoons_mean_nn}
\includegraphics[width=.24\textwidth]{qualitative_twomoons_aggl}
\includegraphics[width=.24\textwidth]{qualitative_twomoons_mst} \\ 
\caption{Comparison of $k$-Means (left), MeanNN (center left), single link
(center right) and ITM (right) on four synthetic datasets.  Without the need to
tune parameters, ITM can adjust to different cluster shapes.  MeanNN is able to
recover non-convex clusters (third row) but often produces similar results to
$k$-Means (second and last row). Single link clustering is very sensitive
to noise, as it does not take cluster size into account.}
\label{fig:qualitative}
\end{figure}

@@

A comparison of ITM, MeanNN and the baseline methods, $k$-Means and 
single link agglomerative clustering, in terms of their objective, 
optimization and complexity can be found in Table~\ref{nowotab}. 
We implemented the ITM clustering procedure as well as MeanNN in Python.  We
used the $k$-Means implementation available in the scikit-learn
library~\citep{pedregosa2011scikit}. The source
code is available online\footnote{\url{https://github.com/amueller/information-theoretic-mst}}.

@@

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lccc}
\toprule
Algorithm &     Objective &     Deterministic&      Complexity \\
\cmidrule{1-4}
$k$-Means &     $\displaystyle \sum_y \sum_{i, y_i = y} \| x_i - \mu_y \|^2$ & No  & $O(nk)$ per iteration%
\footnote{The worst-time complexity of the Lloyd-Algorithm is exponential~\cite{arthur2006slow}, though online algorithm are observed to converge in linear time~\cite{bottou1995convergence}.}
\\
MeanNN &    $\displaystyle \sum_y \log\left(\frac{1}{|\mathbf{x}_y|}\sum_{i,j, y_i=y_j=y} \| x_i - x_j \|^2 \right)$ & No & $O(n^2)$ per iteration\\
Single Link &   -- &    Yes    &    $O(n\log n)$\\
ITM & $\displaystyle \sum_{y=0}^k d p(y) \log(\bar{L}_y  ) + p(y) \log{p(y)}$ & Yes & $O(\alpha(n) n \log n + nk)$\\
\bottomrule
\end{tabularx}
\caption{Comparing properties of related algorithms.}\label{nowotab}
\end{table}

@@

We evaluated the experiments using the \emph{adjusted Rand index 
(ARI}~\citep{hubert1985comparing}  popular measures 
of cluster quality~\citep{gomes2010discriminative,kamvar2003spectral}.
The Rand index~\citep{rand1971objective} between two clusterings counts on how
many pairs of points two clusterings agree. The adjusted Rand index contains a
calibration against chance performance.
We also measured \emph{normalized mutual information
(NMI)}~\citep{strehl2003cluster}, but do not report it here, as it resulted in
an identical ranking of the clustering algorithms.

Table~\ref{results} summarizes the results. The two entropy-based methods 
(MeanNN, ITM) have a clear advantage of the other methods, with ITM finding 
better clusterings than MeanNN in the majority of cases.
We see that ITM does well when the intrinsic dimensionality of the data matches
the feature dimension, but degrated otherwise (see ``faces'' and ``usps'').
Estimating the intrinsic dimensionality of the data overcomes this weakness,
and improves resuls in most cases. For all but one dataset, eigher ITM or ITM with
estimated intrinsic dimensionality gives the best results of all considered
algorithms.
%
The single link agglomerative clustering procedure produces reasonable 
results on datasets with little noise and well-separated clusters, but 
fails otherwise.
%
The run time of computing the ITM clustering was dominated by the computation
of the MST of the data.
%
% TODO runtime statements!
% One table datasets, one table methods + runtime?

\begin{table}[t]
\centering
\begin{tabularx}{\linewidth}{@{\extracolsep{\fill}}lrrrccccc}
\toprule
\multicolumn{4}{c}{Dataset} &\multicolumn{4}{c}{Results}\\
\cmidrule{1-4}
\cmidrule{5-9}
Description &     n &    d &   k &  $k$-Means      & MeanNN        & SL            &   ITM        & ITM ID \\
\cmidrule{1-4}                   \cmidrule{5-5}    \cmidrule{6-6}  \cmidrule{7-7} \cmidrule{8-8} \cmidrule{9-9}
digits      &  1797 &   64 &  10 &     0.62 &      0.67            &0.10          &\B{0.85}       &0.73\\ 
faces       &   400 & 4096 &  40 &     0.41 &      0.49            &0.08          &0.02           &\B{0.54}\\ 
iris        &   150 &    4 &   3 &     0.72 &      0.75            &0.55          &\B{0.88}       &0.88\\
usps        &  9298 &  256 &  10 &     0.52 &      0.54            &0.00          &   0.44        &\B{0.64}\\ 
vehicle     &   846 &   18 &   4 &     0.10 &      0.09            &0.00          &\B{0.10}       &0.10\\
vowel       &   990 &   10 &  11 &     0.17 &      0.19            &0.00          &\B{0.20}       &0.19\\
waveform    &  5000 &   21 &   2 & \B{0.37} &      0.30            &0.00          &   0.23        &0.23\\
\bottomrule
\end{tabularx}
\caption{Adjusted Rand Index of $k$-Means, MeanNN, single link agglomerative clustering and
ITM on several benchmark datasets (higher is better). The best score for
each dataset is printed in bold.}\label{results}
\end{table}

% TODO more experiments: mnist
% todo segmentation unsupervised
% TODO bag of word experiment?
% report times on experiments?

\section{Summary}
In this summary we proposed the use of a minimum spanning tree based,
non-parametric entropy estimator in information theoretic clustering, ITM\@.
Thereby we extended the work of \citet{faivishevsky2010nonparametric} to a more
flexible and efficient entropy estimate.  We proposed an approximate optimization
method by formulating the clustering problem as a search over graphs.
The resulting algorithm is deterministic and has sub-quadratic run time.
%
Empirical comparisons showed that the proposed method outperforms standard
algorithms and the non-parametric entropy based clustering of
\citep{faivishevsky2010nonparametric} on multiple benchmark datasets. We
demonstrated that ITM is able to detect non-convex clusters,
even in the presence of noise.
%
In contrast to other algorithms that can handle non-convex clusters, ITM has no
tuning parameters, as the objective presents a natural trade-off between
balancing cluster sizes and enforcing intra-cluster similarity.
%
A limitation of the proposed algorithm is that it is based on the assumption 
of an absolute continuous data distribution. We show that this limitation can
be overcome in practice by estimating the intrinsic dimensionality of the data. 
%
%In future work we plan to investigate a way to overcome this limitation, 
%for example by estimating the intrinsic dimensionality of the 
%data~\citep{pettis1979intrinsic}.
%
%We will also investigate optimizations of the objective 
%\eqref{graphobjective} that go beyond the proposed method. 
%Move-making algorithms seem a promising way to refine solutions 
%found by Algorithm~1. Branch and bound techniques could provide 
%an alternative approach.
